---
title: "Rebekah Tweets"
author: "Richard G. Gardiner"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load and Clean Data

```{r, load packages, include = FALSE}
library(readxl)
library(tidyverse)
library(tidytext)
library(stringr)
```

loading the data:
```{r, load data}
tweets <- read_excel("2016 2017 Pres Tweets.xlsx")
```

Capturing if they have a Retweet
```{r, retweets}
tweets$rt <- str_detect(tweets$Tweet, "^RT ")

head(tweets$rt)
```

## Cleaning and removing stop words

Here we are removing text that does not have any real meaning and is extremely common.  These include the most common words like: "the", "and", "or".  Rather than using a regular tokenizer, we are using the tokenizer that was specially created for tweets (Mullen 2016).  
```{r}
remove_reg <- "&amp;|&lt;|&gt;"

tidy_tweets <- tweets %>%
#  filter(!str_detect(text, "^RT")) %>% # this removes any retweets, right now we are keeping them in
  mutate(text = str_remove_all(Tweet, remove_reg)) %>%
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"))
```

I am now creating a dataframe of all tweets that contain a "#".  Then I am saving both as a csv to send to Rebekah
```{r}

hashtags <- tidy_tweets %>%
  filter(str_detect(word, "#"))

#write_csv(tidy_tweets, "tweets4initialLooks.csv")
#write_csv(hashtags, "hashtags.csv")
```

Now we can use the tidy tools to plot the most common words

```{r}
tidy_tweets %>%
  count(word, sort = TRUE) %>%
  filter(n > 50) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

There really isn't anything that scares me.  There is a word at the bottom that I don't really know the meaning of (I believe it is french). Now I want to do this again, but for each candidate:

```{r}
tidy_tweets %>%
  group_by(Candidate) %>%
  count(word, sort = TRUE) %>%
  top_n(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = Candidate)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  facet_wrap(~ Candidate, scales = "free_y") 
```