---
title: "Rebekah Tweets"
author: "Richard G. Gardiner"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load and Clean Data

```{r, load packages, include = FALSE}
library(readxl)
library(tidyverse)
library(tidytext)
library(stringr)
```

loading the data:
```{r, load data}
tweets <- read_excel("2016 2017 Pres Tweets.xlsx")
```

Capturing if they have a Retweet
```{r, retweets}
tweets$rt <- str_detect(tweets$Tweet, "^RT ")

head(tweets$rt)
```

## Cleaning and removing stop words

Here we are removing text that does not have any real meaning and is extremely common.  These include the most common words like: "the", "and", "or".  Rather than using a regular tokenizer, we are using the tokenizer that was specially created for tweets (Mullen 2016).  
```{r}
remove_reg <- "&amp;|&lt;|&gt;"

tidy_tweets <- tweets %>%
#  filter(!str_detect(text, "^RT")) %>% # this removes any retweets, right now we are keeping them in
  mutate(text = str_remove_all(Tweet, remove_reg)) %>%
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"))
```

I am now creating a dataframe of all tweets that contain a "#".  Then I am saving both as a csv to send to Rebekah
```{r}

hashtags <- tidy_tweets %>%
  filter(str_detect(word, "#"))

#write_csv(tidy_tweets, "tweets4initialLooks.csv")
#write_csv(hashtags, "hashtags.csv")
```


Now we can use the tidy tools to plot the most common words
```{r}
tidy_tweets %>%
  count(word, sort = TRUE) %>%
  filter(n > 50) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

There really isn't anything that scares me.  There is a word at the bottom that I don't really know the meaning of. Now I want to do this again, but for each candidate:

```{r}
tidy_tweets %>%
  group_by(Candidate) %>%
  count(word, sort = TRUE) %>%
  top_n(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = Candidate)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  facet_wrap(~ Candidate, scales = "free") 

ggsave("Most Common Words.jpeg")
```



## January 21, 2019

I am looking at Rebekah's work on the hashtags.  It is a great step forward by taking out the hashtags and removing the weird characters that sometimes occur, one potential problem I see is that many of the hastags are not separated into individual words ("borderwall").  The reason this does not work for sentiment analysis is because the sentiment analysis dictionary looks for exact matches.  So if the dictionary sees "borderwall" it will come back as not having a match when in reality it should be matched with "border" and "wall".  Now this might not be the most important because the hashtags are found in the raw count for each individual (the figure right above), and they might not even have a sentiment tied to the words.  I am going to try to see what can be done with what we currently have.

### Taking out the hashtags

This takes out the actual "#" but keeps the words together.  This will at least partially fix the problem.
```{r}
tidy_tweets$word <- str_replace(tidy_tweets$word, "#", "")
```

```{r}
sentiments <- tidy_tweets %>%
  left_join(get_sentiments("bing"), by = "word")

sentiments$positive <- ifelse(sentiments$sentiment == "positive", 1, 0)
sentiments$negative <- ifelse(sentiments$sentiment == "negative", 1, 0)

sentiments %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  filter(word != "trump") %>% # trump is listed as positive, so I took it out
  top_n(10, positive) %>%
  mutate(word = reorder(word, positive)) %>%
  ggplot(aes(word, positive, fill = Candidate)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Most Common Positive Words by Candidate")

ggsave("Most Common Positive Words.jpeg")
```

```{r}
sentiments %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  filter(word != "trump") %>% # trump is listed as positive, so I took it out
  top_n(10, negative) %>%
  mutate(word = reorder(word, negative)) %>%
  ggplot(aes(word, negative, fill = Candidate)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Most Common Negative Words by Candidate")

ggsave("Most Common Negative Words.jpeg")

```

```{r}
sentiments %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  arrange(desc(positive)) %>%
  ungroup() %>%
  filter(!str_detect(word, "trump")) %>%
  group_by(Candidate) %>%
  mutate(sentiment_score = positive - negative) %>%
  filter(!is.na(sentiment_score)) %>%
  summarise(total = sum(sentiment_score))
```

Trump was by far more negative than Clinton whereas Macron was about the same as Le Pen, but this is likely due to the nature of the unigram analysis and the influence of the translation.

### Frequencies

Now let's caculate word frequencies for each person.  First, we group by person and count how many times each person used each word.  Then use `left_join()` to add a column of the totla number of words used by each person.  Finally we calculate a frequency for each person and word.

```{r}
frequency <- tidy_tweets %>%
  group_by(Candidate) %>%
  filter(!str_detect(word, "^@")) %>%
  count(word, sort = TRUE) %>%
  left_join(tidy_tweets %>%
              group_by(Candidate) %>%
              summarise(total = n())) %>%
  mutate(freq = n/total)

frequency
```


In order to plot the information learned above we use use the `spread()` function to make a differently shaped data frame:

```{r}
frequency <- frequency %>%
  select(Candidate, word, freq) %>%
  spread(Candidate, freq) %>%
  arrange(Clinton, Trump, Macron, `Le Pen`)

frequency
```

```{r}
library(scales)

ggplot(frequency, aes(Clinton, Trump)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = .25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  theme_minimal() +
  labs(title = "Figure 5: Shared Topics, Clinton and Trump") +
  theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.5))

ggsave("Frequency Alignment.jpeg")
```

```{r}
ggplot(frequency, aes(`Le Pen`, Macron)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = .25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  theme_minimal() +
  labs(title = "Figure 6: Shared Topics, Le Pen and Macron") +
  theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.5))

ggsave("Frequency Alignment France.jpeg")
```

Words near the line are used with about equal frequencies by both individuals.  While words far away from the line are used much more by one person compared to the other.  Words, hashtags, and usernames that appear in this plot are ones that have been used by both individuals at least once in a tweet.






## Revisions for R&R

```{r}
words <- c("Trump", "Donald", "Vote", "Make", "President", "Women", "Just", 
           "Election", "POTUS")
n_mentions <- c(319, 163, 144, 109, 108, 79, 88, 82, 72)

cbind(words, as.numeric(n_mentions)) %>%
  as_tibble() %>%
  mutate(words = fct_reorder(words, desc(n_mentions))) %>%
  ggplot(aes(x = words, y = n_mentions)) +
  geom_col() +
  labs(x = "", y = "",
       title = "Figure 1: Frequency of Key Words - \nClinton 2016",
       caption = "N = 484") +
  coord_flip() +
  geom_text(aes(label = n_mentions), hjust = -0.3) +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  scale_y_continuous(breaks = seq(0, 350, 50), labels = c("0", "50", "100", "150", "200",
                                                          "250", "300", "350"), limits = c(0, 350)) 

ggsave("figure 1.png")
```

```{r}
words2 <- c("Media Rigged or Distored", "#MAGA or Make America Safe", "Voting Instructions", "#DrainTheSwamp AND Hillary or Clinton", "#DrainTheSwamp", "Clinton", "Thank", 
           "Middle East/Terrorism", "Crooked Hillary", "Hillary")
n_mentions2 <- c(16, 52, 37, 27, 70, 84, 95, 6, 57, 95)

cbind(words2, as.numeric(n_mentions2)) %>%
  as_tibble() %>%
  mutate(words2 = fct_reorder(words2, desc(n_mentions2))) %>%
  ggplot(aes(x = words2, y = n_mentions2)) +
  geom_col() +
  labs(x = "", y = "",
       title = "Figure 2: Frequency of Key Words - \nTrump 2016",
       caption = "N = 646") +
  coord_flip() +
  geom_text(aes(label = n_mentions2), hjust = -0.3) +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  scale_y_continuous(breaks = seq(0, 100, 10), limits = c(0, 105)) 

ggsave("figure 2.png")
```


```{r}
values3 <- c("", "NF Policy", "  ", "Negative Macron", "     ", "Nationalism", 
             "       ","EU, Anti Globalization", "         ", 
             "Anti - Islam/Islam Terror", "           ", "ChoisirlaFrance", 
             "             ", "Macron")
number3 <- c(26, 35, 37, 61, 34, 44, 55, 49, 54, 20, 48, 51, 82, 172)
reordering <- c(1:14)

cbind(values3, number3, reordering) %>%
  as_tibble() %>%
  mutate(number3 = as.numeric(number3),
         reordering = as.numeric(reordering),
         values3 = fct_reorder(values3, desc(reordering))) %>%
  ggplot(aes(x = values3, y = number3)) +
  geom_col() +
  geom_text(aes(label = number3), hjust = -0.3) +
  coord_flip() +
  theme_light() +
  labs(x = NULL, y = NULL,
       title = "Figure 3: Frequency of Key Words - Marine Le Pen \n2017",
       caption = "N = 499") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  ylim(0, 200)

ggsave("figure 3.png")
```

```{r}
cbind(values3, number3, reordering) %>%
  as_tibble() %>%
  mutate(number3 = as.numeric(number3),
         reordering = as.numeric(reordering),
         values3 = fct_reorder(values3, desc(number3))) %>%
  ggplot(aes(x = values3, y = number3)) +
  geom_col() +
  geom_text(aes(label = number3), hjust = -0.3) +
  coord_flip() +
  theme_light() +
  labs(x = NULL, y = NULL,
       title = "Figure 3 (ATTEMPT 2): Frequency of Key Words - Marine Le Pen \n2017",
       caption = "N = 499") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  ylim(0, 200)

ggsave("figure 3 (ATTEMPT2.png")
```



```{r}
values4 <- c("Islan, Islamism", "  ", "Terrorism", "    ", "Youth, Education, Employment", 
             "      ", "Domestic Values","        ", "France Heritage", 
             "          ", "Government Reform", "            ", 
             "Economic & Social Policies")
number4 <- c(4, 11, 16, 20, 27, 27, 28, 30, 39, 53, 57, 74, 191)
reordering4 <- c(1:13)

cbind(values4, number4, reordering4) %>%
  as_tibble() %>%
  mutate(number4 = as.numeric(number4),
         reordering4 = as.numeric(reordering4),
         values4 = fct_reorder(values4, desc(reordering4))) %>%
  ggplot(aes(x = values4, y = number4)) +
  geom_col() +
  geom_text(aes(label = number4), hjust = -0.3) +
  coord_flip() +
  theme_light() +
  labs(x = NULL, y = NULL,
       title = "Figure 4: Frequency of Key Words - Macron\n2017",
       caption = "N = 703") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  ylim(0, 250)

ggsave("figure 4.png")
```





```{r}
ggplot(frequency, aes(Clinton, Trump)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = .25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  theme_light() +
  labs(title = "Figure 5: Shared Topics, Clinton and Trump") +
  theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.5))

ggsave("Figure 5.png")
```


```{r}
ggplot(frequency, aes(`Le Pen`, Macron)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = .25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  theme_light() +
  labs(title = "Figure 6: Shared Topics, Le Pen and Macron") +
  theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.5))

ggsave("Figure 6.png")
```

```{r}
sentiments %>%
  filter(Candidate %in% c("Clinton", "Trump"),
         word != "trump") %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  top_n(10, positive) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, desc(positive), Candidate)) %>%
  ggplot(aes(x = word, y = positive, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered() +
  scale_fill_manual(values = c("red2", "blue2")) +
  facet_wrap(~ Candidate, scales = "free_y") +
  labs(x = NULL, y = NULL,
       title = "Figure 7: Positive Framing, American Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5)) 

ggsave("figure 7.png")

sentiments %>%
  filter(!is.na(sentiment)) %>%
  select(word, sentiment)
```


```{r}
sentiments %>%
  filter(Candidate %in% c("Clinton", "Trump")) %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  top_n(10, negative) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, desc(negative), Candidate)) %>%
  ggplot(aes(x = word, y = negative, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered() +
  scale_fill_manual(values = c("red2", "blue2")) +
  facet_wrap(~ Candidate, scales = "free_y") +
  labs(x = NULL, y = NULL,
       title = "Figure 8: Negative Framing, American Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5)) 

ggsave("figure 8.png")
```



```{r}
sentiments %>%
  filter(Candidate %in% c("Macron", "Le Pen")) %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  top_n(10, positive) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, desc(positive), Candidate)) %>%
  ggplot(aes(x = word, y = positive, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free_y") +
  labs(x = NULL, y = NULL,
       title = "Figure 9: Positive Framing, French Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5)) 

ggsave("figure 9.png")
```

```{r}
sentiments %>%
  filter(Candidate %in% c("Macron", "Le Pen")) %>%
  group_by(Candidate, word) %>%
  summarise(positive = sum(positive),
            negative = sum(negative)) %>%
  top_n(10, negative) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, desc(negative), Candidate)) %>%
  ggplot(aes(x = word, y = negative, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free_y") +
  labs(x = NULL, y = NULL,
       title = "Figure 10: Negative Framing, French Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10))

ggsave("figure 10.png")
```


### New Research








## Side research not to be included in final:

The charts above got me asking: how often did the candidate reference the other person?
```{r}
trump <- tidy_tweets %>%
  filter(str_detect(word, "^trump"))

table(trump$Candidate)

hillary <- tidy_tweets %>%
  filter(str_detect(word, "^hillary"))
table(hillary$Candidate)


table(tweets$Candidate)
```

I thought the second to last one was interesting so I wanted to quickly check the usage, and found that Clinton has the most tweets (by far) of any candidate.  This is why we are getting the outcome above.  Can't probably use this in a report.




### Re-doing figures 7-10 based on afinn


```{r}
afinn_sentiments <- tidy_tweets %>%
  left_join(get_sentiments("afinn"), by = "word") %>%
  filter(!is.na(value))
```








```{r}
afinn_sentiments %>%
  filter(Candidate %in% c("Trump", "Clinton")) %>%
  group_by(Candidate, word, value) %>%
  count(word) %>%
  mutate(impact = value * n) %>%
  ungroup() %>%
  group_by(Candidate) %>%
  top_n(n = 10, wt = impact) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, impact, Candidate)) %>%
  ggplot(aes(word, impact, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  xlab(NULL) +
  labs(y = "Impact") +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Figure 7: Most Strongly Empahsized Positive Words \nAmerican Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) 

ggsave("Figure 7 - afinn dictionary.png")
```

```{r}
afinn_sentiments %>%
  filter(Candidate %in% c("Trump", "Clinton")) %>%
  group_by(Candidate, word, value) %>%
  count(word) %>%
  mutate(impact = value * n) %>%
  ungroup() %>%
  group_by(Candidate) %>%
  top_n(n = 10, wt = -impact) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, impact, Candidate)) %>%
  ggplot(aes(word, impact, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  xlab(NULL) +
  labs(y = "Impact") +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Figure 8: Most Strongly Empahsized Negative Words \nAmerican Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) 

ggsave("Figure 8 - afinn dictionary.png")
```


```{r}
afinn_sentiments %>%
  filter(Candidate %in% c("Macron", "Le Pen")) %>%
  group_by(Candidate, word, value) %>%
  count(word) %>%
  mutate(impact = value * n) %>%
  ungroup() %>%
  group_by(Candidate) %>%
  top_n(n = 10, wt = impact) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, impact, Candidate)) %>%
  ggplot(aes(word, impact, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  xlab(NULL) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Figure 9: Most Strongly Empahsized Positive Words \nFrench Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  scale_fill_manual(values = c("#9999CC", "#66CC99"))

ggsave("Figure 9 - afinn dictionary.png")
```


```{r}
afinn_sentiments %>%
  filter(Candidate %in% c("Macron", "Le Pen")) %>%
  group_by(Candidate, word, value) %>%
  count(word) %>%
  mutate(impact = value * n) %>%
  ungroup() %>%
  group_by(Candidate) %>%
  top_n(n = 10, wt = -impact) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, impact, Candidate)) %>%
  ggplot(aes(word, impact, fill = Candidate)) +
  geom_col(show.legend = FALSE) +
  xlab(NULL) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Figure 10: Most Strongly Empahsized Negative Words \nFrench Candidates") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) +
  scale_fill_manual(values = c("#9999CC", "#66CC99"))
  
ggsave("Figure 10 - afinn dictionary.png")
```




```{r}
afinn_sentiments %>%
  group_by(Candidate, word, value) %>%
  count(word) %>%
  mutate(impact = value * n) %>%
  ungroup() %>%
  group_by(Candidate) %>%
  top_n(n = 10, wt = abs(impact)) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, impact, Candidate)) %>%
  ggplot(aes(word, impact, fill = Candidate)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  scale_x_reordered() +
  facet_wrap(~ Candidate, scales = "free") +
  ggtitle("Most Impactful Words by Candidate")

# ggsave("afinn most impactful.png")
```

```{r}
afinn_sentiments %>%
  filter(value < 0) %>%
  distinct(word, value)
```

### overall sentiment of tweets

```{r}
afinn_sentiments %>%
  group_by(Tweet, Candidate) %>%
  summarise(net_value = sum(value),
            number_words = ) 

afinn_sentiments_zeroes <- tidy_tweets %>%
  left_join(get_sentiments("afinn"), by = "word") %>%
  mutate(text = str_remove_all(Tweet, remove_reg)) %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"),
         !word %in% c("rt"),
         !str_detect(word, "@|http|â|[:number:]|ð")) 

afinn_sentiments_zeroes %>%
  group_by(Tweet, Candidate) %>%
  mutate(value = ifelse(is.na(value), 0 ,value)) %>%
  summarise(net_value = sum(value),
            number_words = n()) %>%
  ungroup() %>%
  group_by(Candidate) %>%
  summarise(average_net_value = mean(net_value),
            average_words = mean(number_words)) %>%
  mutate(Candidate = fct_reorder(Candidate, average_net_value)) %>%
  ggplot(aes(x = Candidate, y = average_net_value)) +
  geom_col() +
  labs(x = "", y = "Average Net Sentiment of a Tweet",
       title = "Average Net Sentiment of a Tweet by Candidate",
       subtitle = "Lower Values Indicate More Negative Speech") +
  coord_flip() +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        plot.caption = element_text(size = 11, hjust = 0.5),
        axis.ticks = element_blank()) 

# ggsave("average tweet sentiment.png")
```

